Economic Theory of Fertility Explains Modern Natural Selection

### 2020-11-19 why-negative-selection.Rmd
correct text

Tables \@ref(tab:tbl-siblings-by-period) and
\@ref(tab:tbl-children-by-period) summarize the results. There is no
change in natural selection within the parents' generation. In the
respondents' generation, effect sizes were significantly larger in absolute size among the late-born for five PGS: autism, cognitive ability, EA2, EA3 and
extraversion. These changes are inconsistent with the intergenerational change, 
where effect sizes were if anything larger among the earlier, parents' generation.
Three PGS showed significant changes in sign: alcohol use
(positive to negative); conscientiousness (negative to positive); and
type II diabetes (negative to positive). Overall, there is weak evidence for
change over time, and the clearest result is that the direction of selection is
broadly consistent.

>>>>

Tables \@ref(tab:tbl-siblings-by-period) and
\@ref(tab:tbl-children-by-period) summarize the results. There is no
change in natural selection within the parents' generation. In the
respondents' generation, effect sizes were significantly larger in absolute size among the late-born for four PGS: cognitive ability, EA2, EA3 and
extraversion. These changes are inconsistent with the intergenerational change, 
where effect sizes were if anything larger among the earlier, parents' generation.
Three PGS showed significant changes in sign: alcohol use
(positive to negative); conscientiousness (negative to positive); and
type II diabetes (negative to positive). Overall, there is weak evidence for
change over time, and the clearest result is that the direction of selection is
broadly consistent.
